---
title: "Diego González Farias"
author: 
date: 
output:
  html_document:
    fig_width: 10
    fig_height: 6
    theme: readable
    toc: true
   
       
---

***

<style type="text/css">

h1.title {
  font-size: 38px;
  font-family: "Times New Roman", Times, serif;
  color: Black ;
  text-align: center;
}

/* Agregar un marco a toda la hoja */
body {
  border: 1px solid black;
  margin: 10px; /* Márgenes del marco */
  padding: 10px; /* Espacio dentro del marco */
}


</style>




```{r echo = FALSE, out.width='50%', fig.align='center'}

library(png)
library(grid)

library(png)
library(grid)
img <- readPNG("foto_diego.png")
grid.raster(img)

```



*** 

# *About me*

***

I am currently working at Convert Solutions, a company based in Guadalajara, Jalisco. In my role, I specialize in talent acquisition for operational and administrative positions. I have a track record of successfully identifying and attracting top talent to meet the organization's staffing needs.

Furthermore, I actively contribute to various Human Resources tasks, leveraging my expertise in areas such as employee onboarding, performance management, and HR policy development. I have a strong understanding of best practices in these areas and strive to ensure that our HR processes align with industry standards and support the overall success of the company.

In addition to my HR responsibilities, I also contribute part-time as a continuous improvement engineer. This role allows me to utilize Lean Six Sigma methodologies and tools to identify process inefficiencies, streamline workflows, and drive operational excellence. By implementing data-driven solutions and facilitating change management, I contribute to enhancing productivity and overall business performance.

In my role, I leverage my proficiency in SQL, R, VBA, and DAX to filter and analyze substantial amounts of data, transforming it into actionable insights for the organization. I am passionate about process improvement and have a strong background in Lean Manufacturing tools and process standardization to reduce variability through Six Sigma methodologies.

Currently, I am pursuing a degree in accounting and recently obtained my Green Belt Certification, with a Black Belt diploma (certification in progress). Furthermore, I am expanding my knowledge in R, SQL, and Python to further enhance my analytical capabilities.

*** 



***

# *Job History*

```{r echo = FALSE } 
knitr::opts_chunk$set(echo = TRUE , warning = FALSE , message = FALSE  )
``` 




```{r echo = FALSE }
# Cargar las librerías
library(ggplot2)
library(plotly)

# Crear la tabla de datos
datos_laborales <- data.frame(
  Año = c(2016, 2017, 2018, 2022, 2023),
  Empresa_Puesto = c(
    "Beliveo Customer Service Representative",
    "Teleperformance- Customer Service Representative",
    "TTEC Customer Service Representative",
    "TTEC Talent Acquisition Specialist",
    "Convert Solutions- Talent Acquisition Specialist"
  ), 
  Description= c(
    "I started my work history at this great Call Center where I practiced my English, Customer Service Skills and worked as a Billing Representative", 
    " I then moved to another great Call Center where I had the oportunity to work with Bulk Accounts, improved my sales skills and learn to use multiple tools like Zendesk and CSR", 
    " - Assist customers for a car-sharing company in different scenarios during 
rental time. 
- Coordinate Roadside assistance and work with different vendors to find a 
solution effective and in a timely manner.",
    " Responsible for the hiring process by performing reference checks, 
background checks, screening resumes, interviews, and assessments. 
- Completing paperwork for each individual hire. 
- Coordinate with management to find the best candidate for any position 
needed within the company.
- Developed and implemented a dynamic dashboard that enabled efficient 
resource allocation for Marketing and Talent Acquisition teams by 
identifying the most effective candidate sources.",
    " Responsible for the full operational, administrative, and 
management recruiting cycle. 
- HR Data Analytics and Dashboard management for multiple internal 
clients using PowerBI and Excel.
- Automation of processes using tools like Power Automate and 
Power Apps.
- I was able to provide insights for multiple KPI´s for HR and create 
internal tools for employee management.
- Actively support the Continuous Improvement Area in implementing 
Sustainable Flow Manufacturing (SFM) principles and utilizing Lean 
Six Sigma (LSS) tools to enhance Overall Equipment Efficiency (OEE).
- Drive the implementation of Single-Minute Exchange of Die (SMED) 
techniques to minimize downtime during production changeovers.
- Develop and maintain databases and worksheets to monitor daily 
production results, enabling proactive decision-making when goals 
are not met."
  )
)

# Establecer el orden deseado de los niveles del factor Empresa_Puesto
datos_laborales$Empresa_Puesto <- factor(datos_laborales$Empresa_Puesto, levels = (datos_laborales$Empresa_Puesto))

# Crear el gráfico ggplot
grafico_ggplot <- ggplot(data = datos_laborales, aes(x = Año, y = Empresa_Puesto, group = 1, text = Description)) +
  geom_line(color = "black")+
  geom_point(color = "darkblue",size=3)+
  labs(title = "Interactive plot - Job History ", x = "Year", y = "") +
  theme_minimal()

# Convertir el gráfico a un gráfico interactivo de plotly y configurar la barra de opciones
grafico_interactivo <- ggplotly(grafico_ggplot) %>%
  config(displayModeBar = FALSE)

# Gráfico interactivo
grafico_interactivo

```



***



***



# *Tools I use*

```{r echo = FALSE } 
knitr::opts_chunk$set(echo = TRUE , warning = FALSE , message = FALSE  )
```


```{r echo=FALSE}
# Cargar librerías
library(ggplot2)
library(plotly)

# Crear la tabla de skills y niveles
skills <- c("Excel", "PowerBI", "R", "SQL", "Python")
niveles <- c("Advanced", "Advanced", "Intermediate", "Intermediate", "Basic")

datos_skills <- data.frame(Skill = skills, Nivel = niveles)

# Convertir la columna "Skill" en un factor con el orden deseado
datos_skills$Skill <- factor(datos_skills$Skill, levels = c("Excel", "PowerBI", "R", "SQL", "Python"))

# Convertir la columna "Nivel" en un factor con el orden inverso
datos_skills$Nivel <- factor(datos_skills$Nivel, levels = c("Basic", "Intermediate", "Advanced"))

# Crear la gráfica de barras con el nuevo orden usando ggplot
grafico_barras <- ggplot(datos_skills, aes(x = Skill, y = Nivel, fill = Nivel)) +
  geom_bar(stat = "identity") +
  labs(title = "", x = "Tool", y = " ")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotar etiquetas del eje x para que sean legibles

# Convertir el gráfico ggplot a un gráfico interactivo usando plotly
grafico_interactivo <- ggplotly(grafico_barras)

# Mostrar el gráfico interactivo
grafico_interactivo

```



***



***



#  *Certifications*

***

*Live as if you were to die tomorrow. Learn as if you were to live forever *

***

\newline  \newline
\newline  \newline


```{r echo=FALSE }
library(magick)
library(ggplot2)
library(gridExtra)
library(grid)

# Load the images using image_read() and resize them using image_scale() from magick
bb <- image_read("BB.png") %>% image_scale("800x500")
da <- image_read("DA GOOGLE.jpeg") %>% image_scale("800x500")
ex <- image_read("EXCEL.PNG") %>% image_scale("800x500")
gb <- image_read("GB.png") %>% image_scale("800x500")
r <- image_read("R.png") %>% image_scale("800x500")
sc <- image_read("SCRUM.png") %>% image_scale("800x500")
sql <- image_read("SQL.png") %>% image_scale("800x500")
yb <- image_read("YB.jpeg") %>% image_scale("800x500")
ld <- image_read("LD.png") %>% image_scale("800x500")

# Convert the images to 'grob' objects using rasterGrob() from the grid package
bb_grob <- rasterGrob(bb)
da_grob <- rasterGrob(da)
ex_grob <- rasterGrob(ex)
gb_grob <- rasterGrob(gb)
r_grob <- rasterGrob(r)
sc_grob <- rasterGrob(sc)
sql_grob <- rasterGrob(sql)
yb_grob <- rasterGrob(yb)
ld_grob <- rasterGrob(ld)

# Create the mosaic using grid.arrange()
mosaico <- grid.arrange(bb_grob, da_grob, ex_grob, gb_grob, r_grob, sc_grob, sql_grob, yb_grob, ld_grob, ncol = 3)

# Display the mosaic
grid.newpage()
grid.draw(mosaico)


```













# *Contact*


diego.contador.gf@gmail.com

[Linkedin](https://www.linkedin.com/in/diego-gonzalez-farias-248870234/)

[Download my CV](cv.pdf)
